\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual Multi-Loop Integrands

### 2023-09-21 notes/2loopNLSM.tex
l -> \ell in appendix A

The color-stripped Feynman rule for the three-point vertex can be read
off from the Lagrangian \cref{eq:ZMLagrangian}, giving
\begin{equation}
\langle ab\rangle \equiv p_a^\mu \varepsilon_{\mu\nu} p_b^\nu =p_a^0 p_b^1 - p_a^1 p_b^0 = -\langle ba \rangle .
\end{equation}
Unlike $J$-theory and $YZ$-theory, the vertex is (1) functionally symmetric and (2) the kinematic portion
of the vertex is completely anti-symmetric:
\begin{equation}
\cubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue} = \langle 12\rangle = \langle 23\rangle = \langle 31\rangle = -\langle 21\rangle
\end{equation}
This important property is due to momentum conservation alone and does
not need any additional kinematic constraints to satisfy the duality.
To prove off-shell color kinematics duality for any multiplicity and
loop order it is enough to observe that the sum of the off-shell $s$-,
$t$-, and $u$-channel numerators sum to zero
\begin{equation}
\label{eq:ZMJacobi}
\langle ab \rangle \langle cd\rangle +\langle ac \rangle \langle db\rangle +\langle ad \rangle \langle bc\rangle =0 % \delta^{[a}_c\delta^{b]}_d + \delta^{[a}_d\delta^{c]}_b+ \delta^{[a}_b\delta^{d]}_c
\end{equation}
by virtue of the 2D Levi-Civita identity
$\varepsilon_{\mu\nu}\varepsilon_{\rho\sigma} =
\eta_{\mu\rho}\eta_{\nu\sigma}-\eta_{\mu\sigma}\eta_{\nu\rho}$.
Amusingly, \cref{eq:ZMJacobi} is simply a manifestation of the
Schouten identity. Below we provide the double-box and penta-triangle expressions to which we matched our NLSM integrands to in the text:
\be
\ZMBasisDoubleBox =\left[\begin{split}
  \langle (l_1+k_4) l_1 \rangle\langle l_1l_2 \rangle\langle l_2 (l_2+k_1) \rangle  \langle (l_2+k_1)(l_2+k_1+k_2) \rangle 
\\
\langle (l_1+k_3+k_4)(l_2+k_1+k_2) \rangle\langle (l_1+k_3+k_4)(l_1+k_4) \rangle
\end{split}\right]
\ee
\be
\ZMBasisPentaTriangle =\left[\begin{split}
  \langle (l_1+k_4) l_1 \rangle\langle l_1l_2 \rangle\langle l_2 (l_2+k_1) \rangle  \langle (l_2+k_1)(l_1-k_1) \rangle 
\\
\langle (l_1+k_3+k_4)(l_1-k_1) \rangle\langle (l_1+k_3+k_4)(l_1+k_4) \rangle
\end{split}\right]
\ee
Furthermore, since ZM theory manifests color-kinematics duality without any
reference to the on-shell condition, a mass term can be added to ZM
theory without spoiling color-kinematics duality \cite{Cheung:2022mix}. In general, if the
on-shell conditions are not used, color-kinematics duality is
unaffected by the details of the propagator structure.

>>>>

The color-stripped Feynman rule for the three-point vertex can be read
off from the Lagrangian \cref{eq:ZMLagrangian}, giving
\begin{equation}
\langle ab\rangle \equiv p_a^\mu \varepsilon_{\mu\nu} p_b^\nu =p_a^0 p_b^1 - p_a^1 p_b^0 = -\langle ba \rangle .
\end{equation}
Unlike $J$-theory and $YZ$-theory, the vertex is (1) functionally symmetric and (2) the kinematic portion
of the vertex is completely anti-symmetric:
\begin{equation}
\cubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue} = \langle 12\rangle = \langle 23\rangle = \langle 31\rangle = -\langle 21\rangle
\end{equation}
This important property is due to momentum conservation alone and does
not need any additional kinematic constraints to satisfy the duality.
To prove off-shell color kinematics duality for any multiplicity and
loop order it is enough to observe that the sum of the off-shell $s$-,
$t$-, and $u$-channel numerators sum to zero
\begin{equation}
\label{eq:ZMJacobi}
\langle ab \rangle \langle cd\rangle +\langle ac \rangle \langle db\rangle +\langle ad \rangle \langle bc\rangle =0 % \delta^{[a}_c\delta^{b]}_d + \delta^{[a}_d\delta^{c]}_b+ \delta^{[a}_b\delta^{d]}_c
\end{equation}
by virtue of the 2D Levi-Civita identity
$\varepsilon_{\mu\nu}\varepsilon_{\rho\sigma} =
\eta_{\mu\rho}\eta_{\nu\sigma}-\eta_{\mu\sigma}\eta_{\nu\rho}$.
Amusingly, \cref{eq:ZMJacobi} is simply a manifestation of the
Schouten identity. Below we provide the double-box and penta-triangle expressions to which we matched our NLSM integrands to in the text:
\begin{equation}
\ZMBasisDoubleBox =\left[\begin{split}
  \langle (\ell_1+k_4) \ell_1 \rangle\langle \ell_1\ell_2 \rangle\langle \ell_2 (\ell_2+k_1) \rangle  \langle (\ell_2+k_1)(\ell_2+k_1+k_2) \rangle 
\\
\langle (\ell_1+k_3+k_4)(\ell_2+k_1+k_2) \rangle\langle (\ell_1+k_3+k_4)(\ell_1+k_4) \rangle
\end{split}\right]
\end{equation}
\begin{equation}
  \ZMBasisPentaTriangle =\left[
    \begin{split}
      \langle (\ell_1+k_4) \ell_1 \rangle\langle \ell_1\ell_2 \rangle\langle \ell_2 (\ell_2+k_1) \rangle  \langle (\ell_2+k_1)(\ell_1-k_1) \rangle 
      \\
      \langle (\ell_1+k_3+k_4)(\ell_1-k_1) \rangle\langle (\ell_1+k_3+k_4)(\ell_1+k_4) \rangle
    \end{split}
  \right]
\end{equation}
Furthermore, since ZM theory manifests color-kinematics duality
without any reference to the on-shell condition, a mass term can be
added to ZM theory without spoiling color-kinematics duality
\cite{Cheung:2022mix}. In general, if the on-shell conditions are not
used, color-kinematics duality is unaffected by the details of the
propagator structure.
